---
title: "Credit Model Calibration"
author: "Denise Manfredini"
date: "07/02/2020"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#install.packages('BETS','sidrar','ipeadatar','fpp2','astsa','mFilter')

require(BETS)
#library('dplyr')
require(sidrar)
require(fpp2)
require(ggplot2)
require(astsa)
require(gridExtra)
require(mFilter)
require(deflateBR)
require(zoo)
require(seasonal)
require(tsibble)

theme_set(theme_minimal())
ts2csv <- function(x) {
  fname <- paste0(deparse(substitute(x)), ".csv")
  readr::write_csv(tsibble::as_tsibble(x, gather = FALSE), fname)
}

Sys.setenv(X13_PATH = "C:/Users/Denise Manfredini/Documents/R/win-library/3.4/x13as")
# checkX13()
```

Data for the transiiton path calibration.

##  GDP Measured by Components of Demand
<details>
  <summary>Click to expand</summary>

```{r, message=FALSE}
# From IBGE (quarterly)
GDP.sidra <- get_sidra(api='/t/1846/n1/all/v/all/p/last%2075/c11255/90707/d/v585%200')
GDP.sidra = ts(GDP.sidra$Valor,  start=c(2001,01), freq=4)

# Consumption
consumption <- get_sidra(api='/t/1846/n1/all/v/all/p/last%2075/c11255/93404/d/v585%200')
consumption <-ts(consumption$Valor,  start=c(2001,01), freq=4)

# Government Spending
government<- get_sidra(api='/t/1846/n1/all/v/all/p/last%2075/c11255/93405/d/v585%200')
government <-ts(government$Valor,  start=c(2001,01), freq=4)

# Gross Fixed Capital Formation
capitalformation<- get_sidra(api='/t/1846/n1/all/v/all/p/last%2075/c11255/93406/d/v585%200')
capitalformation <-ts(capitalformation$Valor,  start=c(2001,01), freq=4)

# capital stock
stock<- get_sidra(api='/t/1846/n1/all/v/all/p/last%2075/c11255/102880/d/v585%200')
stock <-ts(stock$Valor,  start=c(2001,01), freq=4)

# Exports
exports<- get_sidra(api='/t/1846/n1/all/v/all/p/last%2075/c11255/93407/d/v585%200')
exports <-ts(exports$Valor,  start=c(2001,01), freq=4)

# Imports
imports <- get_sidra(api='/t/1846/n1/all/v/all/p/last%2075/c11255/93408/d/v585%200')
imports <-ts(imports$Valor,  start=c(2001,01), freq=4)


plot.netexports <- autoplot(exports-imports, main='net exports')
plot.investment <- autoplot(stock+capitalformation, main = 'investment')
plot.consumption <-autoplot(government+consumption, main='consumption')
plot.output <- autoplot(GDP.sidra, main='output')
grid.arrange(plot.netexports ,plot.investment , plot.consumption,plot.output, ncol=2)

#GDP.sidra - (stock+capitalformation+government+consumption+exports-imports)
```
</details>
  
       
# Labor and Capital Markets

## Employment and Hours of Work


```diff
+ Population is divided between PIA and PINA.
+ PIA (eng:AP) is divided between PEA and PNEA.
+ PEA (eng:EAP) is divided between employed and unemployed.
```

```{r, message=FALSE}
# Active population
AP <- BETSget(10800,from = "2001-10-31")

# Economically active population
EAP <- BETSget(10810,from = "2001-10-31")

# Employed 
employed <- BETSget(10812, from ="2001-10-31")
unemployed <- BETSget(10811, from="2001-10-31")


employment.pop <- employed/AP

# Hours of Work
#First is march 2002 last value is Feb/2016
 
hours<- get_sidra(api='/t/2166/n110/all/v/1006/p/all/d/v1006%201')
hours <- ts(hours$Valor,  start=c(2002,03), freq=12)



plot.AP <- autoplot(AP, main='active population')
plot.employment.pop <- autoplot(employment.pop, main = 'employment ratio')
plot.hours <- autoplot(hours, main='worked hours (weekly)')
grid.arrange(plot.AP ,plot.employment.pop , plot.hours, ncol=2)
```

## Credit Market

```{r}
# Total
total <- BETSget(20539,from = "2007-03-01", to = "2017-12-31")

total.firms<- BETSget(20540,from = "2007-03-01", to = "2017-12-31")

total.household <- BETSget(20541,from = "2001-01-01", to = "2017-12-31")

# Earmarked
earmarked <-BETSget(20593,from = "2007-03-01", to = "2017-12-31")

earmarked.firms <-BETSget(20594,from = "2007-03-01", to = "2017-12-31")

earmarked.households <-BETSget(20606,from = "2007-03-01", to = "2017-12-31")

# Non-earmarked
nonearmarked <-BETSget(20542,from = "2007-03-01", to = "2017-12-31")

nonearmarked.firms <-BETSget(20543,from = "2007-03-01", to = "2017-12-31")

nonearmarked.households <-BETSget(20570,from = "2007-03-01", to = "2017-12-31")

```
```{r, message=FALSE}
plot.nonearmarked  <- autoplot(nonearmarked/total , main='non-earmarked credit (%total)')
plot.earmarked <- autoplot(earmarked/total, main = 'earmarked credit (%total)')
plot.nonearmarked.firms <- autoplot(nonearmarked.firms/total.firms, main='nonearmarked credit for firms (%firms total)')
plot.earmarked.firms <- autoplot(earmarked.firms/total.firms, main='earmarked credit for firms (%firms total)')
grid.arrange(plot.nonearmarked ,plot.earmarked , plot.nonearmarked.firms, plot.earmarked.firms,ncol=2)


```

## Monthly (%p.m.) start in March 2011 

```{r, message=FALSE}

rate.nonearmarked <- BETSget(25436,from ="2011-04-01",to ="2017-03-01")

rate.earmarked <-BETSget(25481,from ="2011-04-01",to ="2017-03-01")

rate.gap <- rate.nonearmarked/rate.earmarked 
```

```{r, message=FALSE}
interestrate.ne <- cbind(rate.nonearmarked, rate.earmarked)
autoplot(interestrate.ne, facets=FALSE, main='interest rate (% p.m.)')

cbind(max(rate.nonearmarked), max(rate.earmarked))

cbind(min(rate.nonearmarked), min(rate.earmarked))

```



# Adjusting to real values

## Deflate series
 The series are deflated using the IPCA
 
<details>
  <summary>Click to expand</summary>

```{r, message=FALSE}
actual_dates_quarter <- seq.Date(from = as.Date("2001-01-01"), to = as.Date("2019-07-01"), by = "quarter")
gdp_quarter <- deflate(GDP.sidra, actual_dates_quarter , '01/2010', index = 'ipca')

CC <- consumption 
CI <- capitalformation
CX <- (exports-imports)
CG <- government

CC <- deflate(CC, actual_dates_quarter , '01/2010', index = 'ipca')
CI <- deflate(CI, actual_dates_quarter , '01/2010', index = 'ipca')
CX <- deflate(CX, actual_dates_quarter , '01/2010', index = 'ipca')
CG <- deflate(CG, actual_dates_quarter , '01/2010', index = 'ipca')

```
```{r}
plot.netexports.real <- autoplot(CX, main='real net exports')
plot.investment.real <- autoplot(CI, main = 'real investment')
plot.consumption.real <-autoplot(CC+CG, main='real consumption')
plot.output.real <- autoplot(gdp_quarter, main='real output')
grid.arrange(plot.netexports.real ,plot.investment.real , plot.consumption.real,plot.output.real, ncol=2)
```
 </details>
## Per capita and HP filter Series

```{r, message=FALSE}
## Adjust series to 2001 Q4

# AP to quarter
# from 2001/04 to 2015/04 and from thousands to unit
AP_quarter <- 1000*(aggregate(AP, nfrequency=4)/3)

# Adjust time window
AP_quarter_adj <- window(AP_quarter, start = c(2001, 4), end=c(2015,4))
gdp_quarter_adj <- window(gdp_quarter, start = c(2001, 4), end=c(2015,4))
consumption_CC_adj <- window(CC, start = c(2001, 4), end=c(2015,4))
investment_CI_adj <- window(CI, start = c(2001, 4), end=c(2015,4))
government_CG_adj <- window(CG, start = c(2001, 4), end=c(2015,4))
netexports_CX_adj <- window(CX, start = c(2001, 4), end=c(2015,4))
```



```{r}
## Deseasonalize series and divide by population

# Millions to a unit
gdp_final <- (gdp_quarter_adj/AP_quarter_adj)*1000000
gdp_final <- seas(gdp_final)
gdp_final <-final(gdp_final)

investment_final <- (investment_CI_adj/AP_quarter_adj)*1000000
investment_final <- seas(investment_final)
investment_final <-final(investment_final)

consumption_final <- (consumption_CC_adj/AP_quarter_adj)*1000000
consumption_final <- seas(consumption_final)
consumption_final <-final(consumption_final)



government_final <- (government_CG_adj/AP_quarter_adj)*1000000
government_final <- seas(government_final)
government_final <-final(government_final)

netexports_final <- (netexports_CX_adj/AP_quarter_adj)*1000000
netexports_final <- seas(netexports_final)
netexports_final <-final(netexports_final)
```



```{r}
## HP filter

gdp_final_filter <-  hpfilter(gdp_final, freq=6.25,type="frequency")
consumption_final_filter <-  hpfilter(consumption_final, freq=6.25,type="frequency")
investment_final_filter <-  hpfilter(investment_final, freq=6.25,type="frequency")
government_final_filter <-  hpfilter(government_final, freq=6.25,type="frequency")
netexports_final_filter <-  hpfilter(netexports_final, freq=6.25,type="frequency")
```
```{r}
plot.netexports.hp <- autoplot(netexports_final_filter$trend, main='HP filter net exports')
plot.investment.hp <- autoplot(investment_final_filter$trend, main = 'HP filter investment')
plot.consumption.hp <-autoplot(consumption_final_filter$trend+government_final_filter$trend, main='HP filter consumption')
plot.output.hp<- autoplot(gdp_final_filter$trend, main='HP filter output')
grid.arrange(plot.netexports.hp ,plot.investment.hp ,plot.consumption.hp , plot.output.hp,ncol=2)
```

# Population and Technology Discount Factors
*Gamma* is the tecnology discount factor.

*Eta* is the population discount factor.

```{r}
# From 2001-Q4 to 2015-Q4
gamma <- (consumption_final_filter$trend[length(consumption_final)]/consumption_final_filter$trend[1])^(1/length(consumption_final_filter$trend))

# Fix the time in the data
AP <- window(AP, start=c(2001, 12), end=c(2015, 12))

eta <- (AP[length(AP)]/AP[1])^(1/length(AP))

cbind(eta=eta, gamma=gamma)

# consumption per output
# From 2001/Q4 to 2015/Q4
c_y <- (consumption_final_filter$trend+government_final_filter$trend)/gdp_final_filter$trend

i_y <- (investment_final_filter$trend)/gdp_final_filter$trend

cbind('i/y'=round(mean(i_y),2), 'c/y'=round(mean(c_y),2))
```

## Discount factor

*Beta* is the discount factor.

```{r}
rate.credit <-BETSget(25433)
interest.rate<-mean(rate.credit)/100
beta <- 1-((interest.rate+1)^4 -1)
round(beta, digits = 2)
```

# Final Calibration

All series are expressed in per capita terms after dividing by the  population in active age, those aged 15 to 64.

The measure of **GDP** is the current price GDP from the CNT/IBGE deflated by the IPCA
```{r}
y <- log(gdp_final_filter$trend)

cbind(mean=round(mean(y),2), sd = round(sd(y),2))
```

The **capital stock** is measure using *perpetual inventory* method, using the s data on investment, an initial capital stock, and an estimate
of the rate of depreciation  we constructed a series using the accumulation equation for capital.


```diff
+ The initial value is the same measure by Lama (2011), but the ratios are VERY different.
```




```{r}
delta <- 0.05
initial_capital <- 60330
I <- log(investment_final_filter$trend)

k <- matrix(0, nrow = length(I), ncol = 1)
k[1] <- I[1] +(1-delta)*initial_capital

end <- length(I)-1   

   for(jj in 1:end)  {
      k[jj+1] <- investment_final[jj] +(1-delta)*k[jj]
   }
k <- ts(k, frequency=4, start=c(2001,4))
k <- seas(k)
k<-final(k)

cbind(mean=round(mean(log(k)),2), sd = round(sd(log(k))),2)
```

The measure of **consumption** is the sum of consumption and government spending from CNT/IBGE.

```{r}
c <- log(consumption_final_filter$trend + government_final_filter$trend)
cbind(mean=round(mean(c),2), sd = round(sd(c),2))
```

**Investment** is measured as the gross fixed capital formation from CNT/IBGE.

```{r}
i <- log(investment_final_filter$trend)

cbind(mean=round(mean(i),2), sd = round(sd(i),2))
```
**Total hours worked** is measured by the fraction of hours worked by the AP population.
Fraction of employed population is the proportion of employed population to total. population in active age. 

```{r}
Worked.hours<-(mean(hours)/(16*7))*(employment.pop)
Worked.hours<-(aggregate(Worked.hours, nfrequency=4)/3)
Worked.hours<-ts(Worked.hours, frequency=4, start=c(2001,4))
Worked.hours<-seas(Worked.hours)
Worked.hours<-final(Worked.hours)
total.worked.hours <- Worked.hours*AP_quarter_adj

cbind(mean=round(mean(total.worked.hours),2), sd = round(sd(total.worked.hours),2))
```

```{r}
prog <- matrix(0,  length(c),1)
for (jj in 0:length(c))
{prog[jj] <- 1/gamma^jj}

Technological.Progress.Deflator <- ts(prog,  frequency = 4, start = c(2001, 4))

pop <- matrix(0,  length(c),1)
for (jj in 0:length(c))
{pop[jj] <- 1/eta^jj}

Populator.Deflator <- ts(pop,  frequency = 4, start = c(2001, 4))

```
## Real data in Levels (deseasonalized data)


```diff
+  Detrended by the rate of technological progress (gamma).
```

```{r}
c <- (consumption_final+government_final)*Technological.Progress.Deflator
i <- investment_final*Technological.Progress.Deflator
y <- gdp_final*Technological.Progress.Deflator
h <- Worked.hours
xm <- netexports_final*Technological.Progress.Deflator
k <- k*Technological.Progress.Deflator
```
```{r}
plot.c <- autoplot(c, main='consumption')
plot.i <- autoplot(i, main='investment')
plot.y <- autoplot(y, main='output')
plot.h <- autoplot(h, main='hours')
plot.xm <- autoplot(xm, main='net exports')
plot.k <- autoplot(k, main='Capital Stock')
grid.arrange(plot.c, plot.y, plot.h,plot.i, plot.xm, plot.k, ncol=2)
```

## Graphs (introduction)

<details>
  <summary>Click to expand</summary>
  
```{r, warning==FALSE}
# GDP index from BACEN
growth <-BETSget(22109,from = c("2001-10-01"),to = c("2015-12-31"))
y.growth <-(diff(growth)/(growth)[-length(growth)])*100


# Index from data
xm.index<- (xm/xm[1])*100
i.index<- (i/y)*100

xm.index.plot <- ggplot(xm.index, aes(x = time(xm.index), y = xm.index)) +
    geom_line(size=0.7) + 
    theme_minimal()+
    geom_vline(xintercept=2011.5, linetype="dotted")+
  scale_x_continuous(breaks=seq(2002,2015,1), 
                     labels=2002:2015 )+
   theme(axis.text.x = element_text(angle=90, vjust = 0.5),
         legend.title=element_blank(),
        legend.position = c(.4,0.7))+
  xlab("") + 
  ylab("Net Exports (2001Q4 = 100)")
ggsave(file="xmindex.eps")

y.growth.plot <- ggplot(y.growth, aes(x = time(y.growth), y = y.growth)) +
    geom_line(size=0.7) + 
    theme_minimal()+
    geom_vline(xintercept=2011.5, linetype="dotted")+
  scale_x_continuous(breaks=seq(2002,2015,1), 
                     labels=2002:2015 )+
   theme(axis.text.x = element_text(angle=90, vjust = 0.5),
         legend.title=element_blank(),
        legend.position = c(.4,0.85))+
  xlab("") + 
  ylab("GDP growth")
ggsave(file="ygrowth.eps")

i.index.plot <-ggplot(i.index, aes(x = time(i.index), y = i.index)) +
    geom_line(size=0.7) + 
    theme_minimal()+
  scale_x_continuous(breaks=seq(2002,2015,1), 
                     labels=2002:2015 )+
   theme(axis.text.x = element_text(angle=90, vjust = 0.5),
         legend.title=element_blank(),
        legend.position = c(.4,0.7))+
  geom_hline(yintercept=20, color='red', size=0.7)+
  geom_vline(xintercept=2011.5, linetype="dotted")+
  xlab("") + 
  ylab("Investment (%GDP)")
ggsave(file="iindex.eps")

grid.arrange(xm.index.plot,i.index.plot,y.growth.plot, ncol=2)


```

  
```{r, message=FALSE}

rate.plot <- ggplot() +
  geom_area(data = rate.earmarked, aes(x = time(rate.earmarked), y = rate.earmarked, fill="red") , alpha = 1,linetype="dashed") +
  geom_area(data = rate.nonearmarked, aes(x = time(rate.earmarked), y = rate.nonearmarked, fill="grey"), alpha = 0.4, linetype="dashed") +
   geom_line(data = rate.gap, aes(x = time(rate.earmarked), y = rate.gap, linetype="solid"), color="black") +
    geom_line(size=0.7) +
    theme_minimal()+
  scale_x_continuous(breaks=seq(2007,2017,1), 
                     labels=2007:2017 )+
  theme(axis.text.x = element_text(angle=90, vjust = 0.5))+
  xlab("") + 
  scale_fill_manual(name = '',values = c("grey", "red", "black"),labels = c("non-earmarked credit", "earmarked credit", "ratio"))+
  scale_linetype_manual (name ='', values ="solid",labels = "ratio")+
  ylab("interest rate (%p.m.)")+
  ylim(0,5)+
  theme(
    legend.position = c(0, 1.1),
    legend.justification = c("left", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6)
    )
ggsave(file="rateplot.eps")


actual_dates_month <- seq.Date(from = as.Date("2007-03-01"), to = as.Date("2017-12-30"), by = "month")
earmarked.d <- deflate(earmarked, actual_dates_month  , "03-2007", index = 'ipca')
earmarked.d  <- seas(earmarked.d )
earmarked.d  <-final(earmarked.d )

nonearmarked.d <- deflate(nonearmarked, actual_dates_month  , "03-2007", index = 'ipca')
nonearmarked.d  <- seas(nonearmarked.d )
nonearmarked.d  <-final(nonearmarked.d )

earmarked.growth <-(diff(earmarked.d)/(earmarked.d)[-length(earmarked.d)])*100
nonearmarked.growth <-(diff(nonearmarked.d)/(nonearmarked.d)[-length(nonearmarked.d)])*100
```

```{r}
credit.growth.plot <- ggplot() +
  geom_area(data = nonearmarked.growth, aes(x = time(earmarked.growth), y = nonearmarked.growth, fill="red") , alpha = 0.8,linetype="dashed") +
  geom_area(data = earmarked.growth , aes(x = time(earmarked.growth), y = earmarked.growth , fill="grey"), alpha = 0.8, linetype="dashed") +
    geom_line(size=0.7) +
    theme_minimal()+
  scale_x_continuous(breaks=seq(2007,2017,1), 
                     labels=2007:2017 )+
  theme(axis.text.x = element_text(angle=90, vjust = 0.5))+
  xlab("") + 
  scale_fill_manual(name = '',values = c("grey", "red"),labels = c("earmarked credit", "non-earmarked credit"))+
  ylab("growth rate (%)")+
  theme(
    legend.position = c(1,1),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6)
    ) 

ggsave(file="creditgrowth.pdf")


grid.arrange(rate.plot,credit.growth.plot, ncol=2)
```
```{r}
households <- aggregate(BETSget(20606, from = "2008-01-01", to = "2016-12-31"), nfrequency=1)
firms <- aggregate(BETSget(20594, from = "2008-01-01", to = "2016-12-31"), nfrequency=1)
total <- aggregate(BETSget(20593, from = "2008-01-01", to = "2016-12-31"), nfrequency=1)
  
rural <- aggregate(BETSget(20597, from = "2008-01-01", to = "2016-12-31"), nfrequency=1)
realestate <- aggregate(BETSget(20600, from = "2008-01-01", to = "2016-12-31"), nfrequency=1)
BNDES <- aggregate(BETSget(20604, from = "2008-01-01", to = "2016-12-31"), nfrequency=1)
other <- aggregate(BETSget(20605, from = "2008-01-01", to = "2016-12-31"), nfrequency=1)
```

```{r}
table.1 <- ts.union(round(households/total*100,1), round(firms/total*100,1), round(rural/firms*100,1), round(realestate/firms*100,1), round(BNDES/firms*100,1), round(other/firms*100,1))
table.1
#ts2csv(table.1)
```


</details>

## Data in logs
```{r}
consumption2015<-log(c[((as.yearqtr("2015-04")- as.yearqtr("2001-04"))*4+1)])
investment2015<-log(i[((as.yearqtr("2015-04")- as.yearqtr("2001-04"))*4+1)])
output2015<-log(y[((as.yearqtr("2015-04")- as.yearqtr("2001-04"))*4+1)])

consumption2011=log(c[((as.yearqtr("2011-04")- as.yearqtr("2001-04"))*4+1)])
investment2011=log(i[((as.yearqtr("2011-04")- as.yearqtr("2001-04"))*4+1)])
output2011=log(y[((as.yearqtr("2011-04")- as.yearqtr("2001-04"))*4+1)])

mec<-cbind('2011'=consumption2011, '2015'=consumption2015)
mei<-cbind('2011'=investment2011, '2015'=investment2015)
meo<-cbind('2011'=output2011, '2015'=output2015)
met<- rbind(mec, mei, meo)
rownames(met)<-(c("consumption","investment","output"))
met
```
# Policy design

The transition path will be computed as a transition from the minimum non-earmarked earmarked ration gap to the maximum.

```{r}
pi_p <- seas(rate.nonearmarked/rate.earmarked)
pi_p <-final(pi_p)
pi_p <- (aggregate(pi_p, nfrequency=4)/3)
#pi_p <- ts(pi_p, start = c(2011,2))
pi_p <-  hpfilter(pi_p, freq=6.25,type="frequency")
pi_p <- pi_p$trend

autoplot(pi_p, main='non-earmarked earmarked ratio')

cbind(max=round(max(pi_p),2), min =round(min(pi_p),2))
```

# Final Policy Design Plots


```{r}
rate.nonearmarked <- BETSget(20718,from ="2011-04-01",to ="2016-12-01")
rate.PJ <- BETSget(20725,from ="2000-07-01",to ="2016-12-01")
selic <- BETSget(4189,from ="2000-07-01",to ="2016-12-01")
tjlp <- BETSget(256,from ="2000-07-01",to ="2016-12-01")
tjlp.6 <- tjlp+6
tjlp.15 <- tjlp+1.5

tjlp.union <- ts.union(tjlp,tjlp.6,tjlp.15,selic)
```



Comparing several taxes

```{r}
autoplot(tjlp.union)+
  geom_segment(aes(y = selic), col = "red")+
  xlab("") + 
  ylab("Investment (%GDP)")
#ggsave(file="iindex.eps")
````

Show the equivalence between 20718 and 20725